Describing the C-Space of Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-30 dit-paper_ieee.tex
New plot for CDF (better)

\author{
\IEEEauthorblockN{Thomas Chapeaux\\ and Paul Rodriguez}
\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
Email: tchapeau@ulb.ac.be, paurodri@ulb.ac.be}
\and
\IEEEauthorblockN{Laurent George\\ and ???}
\IEEEauthorblockA{ECE Paris\\
Email}
}
\maketitle

@@

	\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{python-simulation/plots/nofpdit.png}
	\end{center}
	\caption{Evolution of the existence of FPDIT with the CDF}
	\label{fig:noFPDIT}
	\end{figure}

@@

	The ratio between the size of the synchronous and asynchronous C-spaces of
	these systems roughly range from 0.95 in the worst case (high utilization, high
	CDF) to 0.85 in the best case (low utilization, low CDF). Note that the value
	of the CDF has a greater influence on this ratio than the system's total
	utilization, but less so when the CDF is lower. It is also important to note
	that even though a 0.95 ratio may not seem much, the synchronous C-spaces of
	the systems contain many dominated WCET vectors, and only those that are
	pareto-optimal (i.e. non-dominated) actually matter to the designer of the system.
	Using the asynchronous C-space instead will relax some constraints and therefore add new acceptable
	solutions that will dominate solutions that were previously non-dominated,
	increasing the quality of the WCET pareto-front.

>>>>

\author{
\IEEEauthorblockN{Thomas Chapeaux and Paul Rodriguez}
\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
Email: tchapeau@ulb.ac.be, paurodri@ulb.ac.be}
\and
\IEEEauthorblockN{Laurent George and ???}
\IEEEauthorblockA{ECE Paris\\
Email}
}
\maketitle

@@

	\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{python-simulation/plots/nofpdit_3.eps}
	\end{center}
	\caption{Evolution of the existence of FPDIT with the CDF}
	\label{fig:noFPDIT}
	\end{figure}

@@

	The ratio between the size of the synchronous and asynchronous C-spaces of
	these systems roughly range from 0.95 in the worst case (high utilization, high
	CDF) to 0.85 in the best case (low utilization, low CDF). Note that the value
	of the CDF has a greater influence on this ratio than the system's total
	utilization, but less so when the CDF is lower. It is also important to note
	that even though a 0.95 ratio may not seem much, the synchronous C-spaces of
	the systems contain many dominated WCET vectors, and only those that are
	in the border (i.e. non-dominated) actually matter to the designer of the system.
	Using the asynchronous C-space instead will relax some constraints and therefore add new acceptable
	solutions that will dominate solutions that were previously non-dominated,
	increasing the quality of the C-space border.
